Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-24 PaperVictor.tex
Atendi observaciones

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional structures with less
than 100 pairs of layers. We obtained a structure that has the an
omnidirectional spectral width larger than those previously
reported.\notaL{Es cierto?}\notaL{Quité los acrónimos del resumen}
\end{abstract}

@@

We develop two techniques to design
multilayer photonic structures. In the first, the wavelength
($\lambda _{j}$) to which the $j$-th pair of layers is tuned is determined by
a given function of $j$. Several functions are proposed and their
parameters are optimized to maximize the reflectance $\braket{R}$ averaged over
a given spectral and angular range.
The second technique consisted in stacking
sub-mirrors tuned to different wavelengths, chosen so that their
spectral ranges overlap. For each submirror, the spectral range was
obtained from the dispersion relation of a corresponding periodic
structure. The degree of overlap was optimized to maximize $\braket{R}$.
The optimizations were done employing the Minuit module  \cite{minuit}
of the Perl Data Language (PDL) \notaL{cita}.

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$nm and $\lambda_{\min}=3000$nm. \notaL{Any reason
  for these choices? They seem arbitrary.}
%The
%calculations were carried out using the Perl Data Language (PDL)
%\notaL{cita} and
%its interface to the MINUIT \cite{minuit} minimization package.
\notaL{Creo que ya habíamos mencionado esto}.
The
optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
are shown in Table \ref{tab:tableA}.
\notaV {En caso de ser necesario: Results for other
  pairs of porosities, $30/76 \% $ and $42/76 \%$, are included as
  supplementary information.}
\begin{table}
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.24    &---      &---     &222   &86.1    &300    &1150    &89\\
      $f_{2}$     &0.37    &1.06     &---     &102   &35.9    &220    &1110    &88\\
      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
      \hline
      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
      $f_{2}$     &1.08    &1.86     &---     &105   &61.7    &2000    &2000    &89\\
      $f_{3}$     &1.01    &1.95     &0.20    &102   &62.3    &2050    &1975    &90\\
    \end{tabular}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral ranges
    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
    of the structure and the omnidirectional spectral
    width and center (ODW and ODC). \notaL{Para el primer rango habría que
      especificar $\lambda_{min}$ también.}}
\end{table}

The function
$f_{3}$ yields after optimization the highest $\braket{R}$ in the
region $\mathcal R_1$ and with the thinnest structure. Furthermore, this
structure has an
omnidirectional spectral band (ODB), defined as the region for which
$R>0.90$ for all angles,
\notaL{Se me ocurre ODW, omnidirectional spectral width, ODB band, ODC center. Si están de
  acuerdo, habría que rotular de nuevo las figuras.}
of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). \notaL{¿Por
  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna
  referencia que defina dicho criterio?} We
synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar reflectance
spectra,\notaL{es correcto spectra aquí, o nos referimos al promedio?}
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    indicate the ODB and the dashed lines
    indicate the quasi-ODB.
    gap.}
\end{figure}

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
	\label{Fig2}
	\begin{center}
		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
	\end{center}
	\caption{Reflectance spectra for non-polarized light calculated and measured at different
	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
        (panel a)  and $S_2$ (panel b). The gray band indicates the
        region where the reflectance is greater than  $0.90$,
        corresponding to the quasi OD band of the
        structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria.
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic
structure in which 54 sub-mirrors were stacked as follows:\notaL{I
  changed to passive to avoid the fact that Agarwal did the stacking} the
first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} tuned to
$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
- \lambda_{j}=2+j$ (with its suitable units)\notaL{This is still
  wrong and/or I don't understand. What are these suitable units? Why
  the mistery? $j$ numbers
  periods or sub-mirrors? Do you mean (2+j) nm, such as the sequence
  $\lambda_1=700$, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
  $\lambda_{54}=700+2*53+54*55/2-1=2290$?}with 4 periods for
each of the following periods.
Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector and $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
photonic band gap within which we
expect a high reflectance, even for a finite system made of only a few periods. This suggests
the following design strategy. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. This is particularly important
for submirrors tuned to shorter wavelengths, for which there is some
absorption. We followed thus two design
strategies: In the first, we considered sub-mirrors each with the same
number $p$ of periods. In the second, a different number of periods was
assigned to each submirror according to the center of its PBG: we chose
a single period for those submirrors $j$ tuned to
$\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
three periods for $650<\lambda_ {j}<800$ nm, and for
$\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para
  cada subespejo?}
In both designs, the degree of overlap of consecutive PBGs was
taken as the parameter to be optimized in order to maximize
the reflectance $\braket{R}$ averaged within the spectral and
angular range $400\text{nm}\le
\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$. \notaL{¿Valdría la pena
  definir este overlap?}

@@

Finally, Table \ref{tab:table3} shows data from some porous silicon based OD
mirrors designed to operate in the NIR
region and the width of the OD bands are compared
with those of the structures
analyzed in the present study. The table reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}. \notaL{Creo que podríamos
  echarla más crema a los tacos, dado que una muestra llega hasta 950, como la de Estevez, pero
  con un ancho mucho mayor, y las otras dos llegan más al azul que las demás muestras previas y
  con mejores anchos de banda}

>>>>

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional structures with less
than 100 pairs of layers. We obtained a structure that has the an
omnidirectional spectral width larger than those previously
reported.\notaL{Es cierto?}\notaL{Quité los acrónimos del resumen}
\notaV{S\'{i}, la estructura m\'{a}s reciente tiene un ODW de 1321 nm (compuesta por LHM) y la \'{u}ltima estructura de SP tiene un ODW de 1000 nm; las nuestras tienen un ODW de 1800 nm.}
\end{abstract}

@@

We develop two techniques to design
multilayer photonic structures. In the first, the wavelength
($\lambda _{j}$) to which the $j$-th pair of layers is tuned is determined by
a given function of $j$. Several functions are proposed and their
parameters are optimized to maximize the reflectance $\braket{R}$ averaged over
a given spectral and angular range.
The second technique consisted in stacking
sub-mirrors tuned to different wavelengths, chosen so that their
spectral ranges overlap. For each submirror, the spectral range was
obtained from the dispersion relation of a corresponding periodic
structure. The degree of overlap was optimized to maximize $\braket{R}$.
The optimizations were done employing the Minuit module  \cite{minuit}
of the Perl Data Language (PDL) \cite{PDL1997}. \notaL{cita} \notaV{Listo}

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm. \notaL{Any reason
  for these choices? They seem arbitrary.} \notaV{El objetivo de elegir la primer regi\'{o} era comparar la estructura optimizada con el espejo blanco obtenido por Ariza \cite{Ariza2012}. La segunda regi\'{o}n la eleg\'{i} porque es uno de los rangos m\'{a}ximos que puedo medir (200-3300) nm. En principio puedo optimizar en una regi\'{o}n m\'{a}s amplia, pero solo quedar\'{i}a en el c\'{a}lculo sin su complemento experimental.}
%The
%calculations were carried out using the Perl Data Language (PDL)
%\notaL{cita} and
%its interface to the MINUIT \cite{minuit} minimization package.
\notaL{Creo que ya habíamos mencionado esto} \notaV{S\'{i}, oraci\'{o}n repetida}.
The
optimized parameters corresponding to the low and high porosities $p_l=0.51$ and $p_h=0.76$
are shown in Table \ref{tab:tableA}.

\begin{table}
  \centering
  \label{tab:tableA}
  \addtolength{\tabcolsep}{-2pt}
    \begin{tabular}{rrrrrrrrrr}
      Class&$\alpha$&$\beta$&A&$\lambda_{min}(nm)$&$N_{p}$&$d(\mu\text{m})$       &ODW(nm)&ODC (nm)&$\braket{R}(\%)$\\
      \hline
      \hline
      $f_{1}$     &0.24    &---      &---     &250&222   &86.1    &300    &1150    &89\\
      $f_{2}$     &0.37    &1.06     &---     &400&102   &35.9    &220    &1110    &88\\
      $\bm{f_{3}}$&\bf 1.23&\bf 0.540&\bf 0.18&\bf 320&\bf 63&\bf 21.6&\bf 250&\bf 1125&\bf 89\\
      \hline
      $\bm{f_{1}}$&\bf 1.20&\bf ---  &\bf --- &\bf ---&\bf 90&\bf 60.4&\bf 2150&\bf 1925&\bf 92\\
      $f_{2}$     &1.08    &1.86     &---  &---  &105   &61.7    &2000    &2000    &89\\
      $f_{3}$     &1.01    &1.95     &0.20  &---  &102   &62.3    &2050    &1975    &90\\
    \end{tabular}
  \caption{Optimized parameters $\alpha$, $\beta$, $A$ and $N_p$ yielding the highest
    reflectance $\braket{R}$ averaged over the spectral ranges
    $\mathcal R_1$ (first block) and $\mathcal R_2$ (second block) and
    the angular range $0-90^\circ$ for the profile classes $f_1$, $f_2$ and
    $f_3$ (Eqs. (\ref{F1}) - (\ref{F3})). We include the thickness $d$
    of the structure and the omnidirectional spectral
    width and center (ODW and ODC). \notaL{Para el primer rango habría que
      especificar $\lambda _{min}$ también.} \notaV{Listo}}
\end{table}

The function
$f_{3}$ yields after optimization the highest $\braket{R}$ in the
region $\mathcal R_1$ and with the thinnest structure. Furthermore, this
structure has an
omnidirectional spectral band (ODB), defined as the region for which
$R>0.90$ for all angles,
\notaL{Se me ocurre ODW, omnidirectional spectral width, ODB band, ODC center. Si están de
  acuerdo, habría que rotular de nuevo las figuras.} \notaV{De acuerdo! Figuras modifocadas.}
of width (ODW) 250 nm centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b). \notaL{¿Por
  qué 90 y no 80 o 95? ¿Es arbitrario? ¿Es un estandard? ¿Hay alguna referencia que defina dicho criterio?} 
\notaV{Alguna referencia que defina como tal este criterio, NO. 
	Sin embargo, hay algunos autores que toman $R>90\%$ como punto 
	de partida para describir sus sistemas multicapa 
	\cite{Xu2018,Ahmed2014,Reiner2000}. Depende de los resultados 
	que hayamos obtenido y qu\'{e} queramos vender}
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
\notaL{es correcto spectra aquí, o nos referimos al promedio?} \notaV{Al promedio}
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\chi_j)$ optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    indicate the ODB and the dashed lines
    indicate the quasi-ODB.
    gap.}
\end{figure}

In Fig. \ref{Fig2}(a) we present the calculated and measured
reflectance for non-polarized light corresponding to sample $S_1$ in the spectral range from 350 to 1400
nm for different angles of
incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$. The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the ODB. Nevertheless, our results allow us to conclude that
the structure has a quasi-ODB from 980 and
1340 nm.
\begin{figure}
	\label{Fig2}
	\begin{center}
		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
	\end{center}
	\caption{Reflectance spectra for non-polarized light calculated and measured at different
	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
        (panel a)  and $S_2$ (panel b). The gray band indicates the
        region where the reflectance is greater than  $0.90$,
        corresponding to the quasi ODB of the
        structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-ODW of 1800 nm
centered at 1880 nm.

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria.
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic
structure in which 54 sub-mirrors were stacked as follows:\notaL{I
  changed to passive to avoid the fact that Agarwal did the stacking} the
first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} \notaV{S\'{i}, as\'{i} lo propuso} tuned to
$\lambda_{1}=700$ nm; the following $j-th$ sub-mirrors were tuned to
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
- \lambda_{j}= \left(2+j \right)$ nm %(with its suitable units)
\notaL{This is still
  wrong and/or I don't understand. What are these suitable units? \notaV{units: nm} Why
  the mistery? \notaV{No cre\'{i} que fuera tan relevante} $j$ numbers
  periods or sub-mirrors? \notaV{$j-th$ sub-mirrors} Do you mean (2+j) nm, such as the sequence
  $\lambda_1=700$, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
  $\lambda_{54}=700+2*53+54*55/2-1=2290$?} 
\notaV{$\lambda_1=700$, $\lambda_2=\lambda_{1}+2+1=703$, $\lambda_3=\lambda_{2}+2+2=704\ldots$
$\lambda_{54}=\lambda_{53}+2+53= 700+2*53+53*54/2= 2237$.}
with 4 periods for
each of the following periods.
Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos \left(KD \right) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector and $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system. This condition corresponds to a
photonic band gap within which we
expect a high reflectance, even for a finite system made of only a few periods. This suggests
the following design strategy. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. This is particularly important
for submirrors tuned to shorter wavelengths, for which there is some
absorption. We followed thus two design
strategies: In the first, we considered sub-mirrors each with the same
number $p$ of periods. In the second, a different number of periods was
assigned to each submirror according to the center of its PBG: we chose
a single period for those submirrors $j$ tuned to
$\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
three periods for $650<\lambda_ {j}<800$ nm, and for
$\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para cada subespejo?}
\notaV{De acuerdo a lo aprendido en las estructuras chirped, se 
	requiere que las estructuras posean pocas bicapas en la 
	regi\'{o} de alta absorci\'{o}n y pueden ir aumentando a 
	medida que disminuye la absorci\'{o}n. Por eso se me hizo 
	sensato proponer esa configuraci\'{o}n en la segunda 
	estrategia de diseño. S\'{i}, si se podr\'{i}a optimizar $p$ 
	para cada sub espejo; sin embargo, corremos el riesgo de 
	obtener una estructura similar a la propuesta por 
	Estrada-Weise \cite{DelRio2018}. Adem\'{a}s, los resultados 
	aqu\'{i} mostrados ya no ser\'{i}an los adecuados.}
In both designs, the degree of overlap of consecutive PBGs was
taken as the parameter to be optimized in order to maximize
the reflectance $\braket{R}$ averaged within the spectral and
angular range $400\text{nm}\le
\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$. \notaL{¿Valdría la pena
  definir este overlap?}
\notaV{No entend\'{i} esta observaci\'{o}n.}

@@

Finally, Table \ref{tab:table3} shows data from some porous 
silicon based OD mirrors designed to operate in the NIR
region and the width of the OD bands are compared with those of 
the structures analyzed in the present study. For example, the ODW 
of the structure $S_1$ is 20 nm wider than that reported by Bruyant, 
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore, 
the ODB of the structure $S_3$ begins at 950 nm like the one 
synthesized by Estevez, et al. \cite{Estevez2009}; however, the width of S3 extends to 2750 
nm. In other words, $S_3$ has ODW 3.55 times higher. Moreover, the 
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6 
\% of the ODW of the S2 and S3 structures. Aditionally, the table 
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}. \notaL{Creo que podríamos
  echarla más crema a los tacos, dado que una muestra llega hasta 950, como la de Estevez, pero
  con un ancho mucho mayor, y las otras dos llegan más al azul que las demás muestras previas y
  con mejores anchos de banda} \notaV{Agregue tres oraciones m\'{a}s}
